---
title: "PokemanageR"
author: "Caratheodory"
date: "v0.31, 7 August 2016"
output: html_document
---

<!-- Alternate table row background colours -->
<style> tr:nth-child(even) {background-color: #f5f5f5;} </style>

```{r SETUP, include=FALSE}

require(knitr)
source("functions.R")

parse_response(file.path("response", "response.bin"), 
               file.path("response", "inventory.txt"))
df <- parse_inventory(file.path("response", "inventory.txt"))

# set target level for powering up
targetLevel <- 30

```

For an explanation of the different fields see [https://github.com/caratheodory/pokemanageR](https://github.com/caratheodory/pokemanageR).

Any comments and feedback are appreciated!


```{r READ GAME DATA, include=FALSE}

# import game data
baseStats <- read.table(file.path("game_data","GAME_MASTER_POKEMON_v0_2.tsv"), header=TRUE, sep="\t")
name <- readLines(file.path("game_data","pokemon_names.txt"), warn=FALSE)
levels <- read.table(file.path("game_data","cp_multipliers.csv"), header=TRUE, sep=",")
stardust <- read.table(file.path("game_data","stardust.tsv"), header=TRUE, sep="\t")
movesets <- read.table(file.path("game_data","movesets_prof_kukui_2016-07-30.csv"), header=TRUE, sep=",")
basicMoves <- read.table(file.path("game_data","basic_moves_prof_kukui_2016-07-30.csv"), header=TRUE, sep=",", stringsAsFactors=FALSE)
chargeMoves <- read.table(file.path("game_data","charge_moves_prof_kukui_2016-07-30.csv"), header=TRUE, sep=",", stringsAsFactors=FALSE)

# convert to lookup table
row.names(basicMoves) <- basicMoves$ID
row.names(chargeMoves) <- chargeMoves$ID

# Add pokemon names
baseStats$Name <- name

# Let's see if the CP formula is correct

df$CpEstimate <- mapply(compute_cp, df$PokemonId, df$IndividualAttack, df$IndividualDefense, df$IndividualStamina, 
                        df$CpMultiplier, df$AdditionalCpMultiplier)
# df[c("Cp", "CpEstimate")]
# nrow(df[df$Cp != df$CpEstimate & df$PokemonId != 0, ])

# Add additional CP statistics
df$CpMin <- mapply(compute_cp_min, df$PokemonId, df$CpMultiplier)
df$CpMax <- mapply(compute_cp_max, df$PokemonId, df$CpMultiplier)
df$CpPercentage <- 1 - (df$CpMax - df$CpEstimate) / (df$CpMax - df$CpMin)

# compute levels
df$Level <- unlist(lapply((df$CpMultiplier + df$AdditionalCpMultiplier), compute_level))

# Add stardust
df$Stardust <- unlist(lapply(df$Level, compute_stardust))

# Add MaxCp
df$MaxCp[df$PokemonId > 0] <- baseStats[df$PokemonId, "MaxCp"]

# Add 
df$CpTarget <- mapply(compute_cp, df$PokemonId, df$IndividualAttack, df$IndividualDefense, df$IndividualStamina, compute_cpmultiplier(30))
df$CpTargetMax <- mapply(compute_cp_max, df$PokemonId, compute_cpmultiplier(30))
df$CpTargetMin <- mapply(compute_cp_min, df$PokemonId, compute_cpmultiplier(30))

# Add Stardust and Candy to levels dataframe
levels$Stardust <- rep(stardust$Stardust, each=4)
levels$Candy <- rep(stardust$Candy, each=4)

# Add DustCost and CandyCost to evolve to targetLevel
df$DustCost <- mapply(compute_dustcost, df$Level, targetLevel)
df$CandyCost <- mapply(compute_candycost, df$Level, targetLevel)

# max evolutions
baseStats <- add_max_evolutions(baseStats)
# baseStats[0:151, c("Name", "Evolution", "EvolutionInt", "MaxEvolutionInt")]

# Add move names
df$Move1 <- as.integer(df$Move1)
df$Move2 <- as.integer(df$Move2)
df$Move1Name <- basicMoves[as.character(df$Move1), "Name"]
df$Move2Name <- chargeMoves[as.character(df$Move2), "Name"]

# add names and max evolution
df$Name[df$PokemonId > 0] <- baseStats$Name[df$PokemonId]
df$Name[df$PokemonId == 0] <- "Egg"
df$Nickname[df$PokemonId == 0] <- "Egg"
df$MaxEvolutionId[df$PokemonId > 0] <- baseStats$MaxEvolutionInt[df$PokemonId]

# add best movesets
df <- add_best_movesets(df)

# Add Cp of evo and evo at target level
df$CpEvo <- mapply(compute_cp, df$MaxEvolutionId, df$IndividualAttack, df$IndividualDefense, 
                   df$IndividualStamina, df$CpMultiplier)

df$CpEvoTarget <- mapply(compute_cp, df$MaxEvolutionId, df$IndividualAttack, 
                         df$IndividualDefense, df$IndividualStamina, compute_cpmultiplier(targetLevel))


```

# Order by PokemonId, PercentagePerfect

This table can be used in conjunction with the view Pokemon > # in the app.

```{r PRINT TABLES 1, echo=FALSE}

output <- df[with(df, order(PokemonId, -PercentagePerfect)), 
   c("PokemonId", "Cp", "Stamina", "IndividualAttack", "IndividualDefense", "IndividualStamina", "PercentagePerfect", "Level", "Nickname")]

kable(output)


```

# Order by GymOffense

Display my best offensive pokemons and the cost to evolve them to target level (30 by default).

```{r PRINT TABLES 2, echo=FALSE}

subdf <- subset(df, PokemonId != 0 & !is.na(GymOffense))

output <- subdf[with(subdf, order(-GymOffense)), 
   c("PokemonId", "Name", "PercentagePerfect", "Cp", "Level", "CpEvoTarget", "DustCost", "GymOffense", "TotalRankOffense", "TotalRankDefense")]
kable(output)

```

# My best Offense and Defense

Display all pokemon/moveset combinations that make it to the top 200 best attackers and defenders.

```{r PRINT TABLES 3, echo=FALSE}

subdf <- subset(df, TotalRankOffense <= 200 | TotalRankDefense <= 200)
output <- subdf[with(subdf, order(-GymOffense)), 
      c("PokemonId", "Name", "PercentagePerfect", "Cp", "Level", "CpEvoTarget", "DustCost", "GymOffense", "TotalRankOffense", "TotalRankDefense")]
kable(output)


```


# Bonus plots

## How does CpMultiplier scale?

```{r PLOTS 1,  echo=FALSE}

plot(levels$CpMultiplier)

```

## Scatterplot of PercentagePerfect vs CpPercentage

```{r PLOTS 2, echo=FALSE}

plot(df[c("PercentagePerfect", "CpPercentage")])

```

## Impact of IVs on CP

```{r PLOTS 3, echo=FALSE}

plot(mapply(compute_cp_max, 16, levels$CpMultiplier), type="b", main="PokemonId 16")
lines(mapply(compute_cp, 16, 7.5, 7.5, 7.5, levels$CpMultiplier), type="b", pch=19)
lines(mapply(compute_cp_min, 16, levels$CpMultiplier), type="b")

```

## IV distribution

```{r PLOTS 4, echo=FALSE}

subdf <- subset(df, PokemonId != 0)
hist(c(subdf$IndividualAttack, subdf$IndividualDefense, subdf$IndividualStamina),
     breaks = seq(-0.5, 15.5, 1), main="IV Histogram", col="lightgrey")

hist(subdf$IndividualAttack + subdf$IndividualDefense +subdf$IndividualStamina,
     breaks = seq(-0.5, 45.5, 1), main="Aggregated IV Histogram", col="lightgrey")


```

## Level distribution

```{r PLOTS 5,  echo=FALSE}

subdf <- subset(df, PokemonId != 0)
hist(subdf$Level, breaks = seq(0.5, 40.5, 1), main="Level Histogram", col="lightgrey")

```

## Investigating the Pokedex IV "bug"

```{r PLOTS 6,  echo=FALSE}

plot(df[c("PokemonId", "IndividualAttack")], pch=15, main="Pokedex# vs IVA")


```



